`r params$doc_title`

### 2022-11-23 scripts/MSc.Rmd
addded performance measures (empSE, coverage, bias-eliminated-coverage, type1error)

t(filter_FTO) %>% kable() #%>% 
  kable_styling(font_size=10)
```

@@

# Dual Y axis: we have 284 IVs, scale them to 5% (y-axis [0;5%]): 3/284 
## https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html
scale_factor <- 4.5/284
df_cum_expl_var <- df_cum_expl_var %>% 
  mutate(
    cum_expl_varX = cum_expl_varX *100, # in percent 
    cum_expl_varX2 = cum_expl_varX2 *100,
    cum_expl_varU = cum_expl_varU *100,
    cum_expl_varY = cum_expl_varY *100,
    count_IVs_scaled = count_IVs*scale_factor)

# plot_data <- df_cum_expl_var %>% 
#   pivot_longer(cols = c(cum_expl_varX, cum_expl_varU, count_IVs_scaled)) %>% 
#   mutate(name = factor(name, labels = c("Number of IVs", "% var(U)", "% var(X)")))
# 
# ggplot(plot_data, aes(x=log10(n), y=value, col=name))+
#   geom_point(alpha=0.6)+
#   geom_line(alpha=0.6)+
#   xlab("log10(N)")+
#   #ylab("% variance explained by IVs")+
#   labs(title = "Figure 1",
#        col='', 
#        caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
#        ) +
#   scale_y_continuous(
#     # Features of the first axis
#     name = "% variance explained by IVs",
#     # Add a second axis and specify its features
#     sec.axis = sec_axis(~./scale_factor, name="Number of IVs")
#   ) + 
#   theme_few()+
#   scale_colour_few() ->fig01
# fig01
# 
# plot_data_b <- df_cum_expl_var %>% 
#   pivot_longer(cols = c(cum_expl_varX2, cum_expl_varU, count_IVs_scaled)) %>% 
#   mutate(name = factor(name, labels = c("Number of IVs", "% var(U)", "% var(X)")))
# 
# ggplot(plot_data_b, aes(x=log10(n), y=value, col=name))+
#   geom_point(alpha=0.6)+
#   geom_line(alpha=0.6)+
#   xlab("log10(N)")+
#   #ylab("% variance explained by IVs")+
#   labs(title = "Figure 1",
#        col='', 
#        caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
#        ) +
#   scale_y_continuous(
#     # Features of the first axis
#     name = "% variance explained by IVs",
#     # Add a second axis and specify its features
#     sec.axis = sec_axis(~./scale_factor, name="Number of IVs")
#   ) + 
#   theme_few()+
#   scale_colour_few() ->fig01_b
# fig01_b
# 
# ggsave(filename = "../output/plots/figure01.png", plot = fig01_b, 
#        width = 10, height = 6, 
#        units = "in"  # default
#        )
# 
# filenamefig01_a <- paste0("../output/plots/", Sys.Date(), "_figure01_a.png")
# filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_b.png")
```

@@

```{r MendelianRandomization-analysis, warning=FALSE}
mr_methods = c("IVW", "median", "mode", "PRESSO", "Robust", "Lasso", "egger", "conmix", "MRMix", "RAPS")
est <- tibble(mr_methods=mr_methods, estimate=NA, se.estimate=NA, time=NA)
numIV <- nrow(my_data_harm)

if (numIV>2){
        mr.obj = MendelianRandomization::mr_input(
          # exposure
          bx = my_data_harm$beta.bmi, 
          bxse = my_data_harm$se.bmi, 
          # outcome
          by = my_data_harm$beta.gbc, 
          byse = my_data_harm$se.gbc, 
          snps = my_data_harm$SNP,
          exposure = "Body mass index",
          outcome = "Gallbladder Cancer"
        )
        # 1. IVW
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_ivw(mr.obj)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="IVW"] = res$Estimate
        est$se.estimate[est$mr_methods=="IVW"] = res$StdError
        est$time[est$mr_methods=="IVW"] = T1-T0
        rm(res)

        # 2. median
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_median(mr.obj)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="median"] = res$Estimate
        est$se.estimate[est$mr_methods=="median"] = res$StdError
        est$time[est$mr_methods=="median"] = T1-T0
        rm(res)
        # 3. mode
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_mbe(mr.obj)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="mode"] = res$Estimate
        est$se.estimate[est$mr_methods=="mode"] = res$StdError
        est$time[est$mr_methods=="mode"] = T1-T0
        rm(res)
        # 4.MR-PRESSO    ## CAVE: 5 minutes per round, consider only calculating for defined thresholds
        T0 = proc.time()[3]
        res <- MRPRESSO:: mr_presso(BetaOutcome = "beta.gbc", 
                    BetaExposure = "beta.bmi", 
                    SdOutcome = "se.gbc", 
                    SdExposure = "se.bmi", 
                    OUTLIERtest = TRUE, 
                    DISTORTIONtest = TRUE, 
                    seed = 20221114,
                    data = as.data.frame(my_data_harm), ## must be a data.frame
                    NbDistribution = 1000,   # must be changed
                    SignifThreshold = 0.05)
        T1 = proc.time()[3]
        if (!is.na(res$`Main MR results`[2,"Causal Estimate"]) & !is.na(res$`Main MR results`[2,"Sd"])){
                est$estimate[est$mr_methods=="PRESSO"] =  res$`Main MR results`[2,"Causal Estimate"]
                est$se.estimate[est$mr_methods=="PRESSO"] = res$`Main MR results`[2,"Sd"]
            } else{
                est$estimate[est$mr_methods=="PRESSO"] =  res$`Main MR results`[1,"Causal Estimate"]
                est$se.estimate[est$mr_methods=="PRESSO"] = res$`Main MR results`[1,"Sd"]
        est$time[est$mr_methods=="PRESSO"] = T1-T0
        rm(res)
        # 5. robust
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_ivw(mr.obj,"random", robust = TRUE)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="Robust"] = res$Estimate
        est$se.estimate[est$mr_methods=="Robust"] = res$StdError
        est$time[est$mr_methods=="Robust"] = T1-T0
        rm(res)
        # 6. MR-Lasso
        T0 = proc.time()[3]
        res = MR_lasso(betaYG = my_data_harm$beta.gbc, betaXG = my_data_harm$beta.bmi, sebetaYG = my_data_harm$se.gbc)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="Lasso"] = res$ThetaEstimate
        est$se.estimate[est$mr_methods=="Lasso"] = res$ThetaSE
        est$time[est$mr_methods=="Lasso"] = T1-T0
        rm(res)
        # 7. Egger
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_egger(mr.obj)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="egger"] = res$Estimate
        est$se.estimate[est$mr_methods=="egger"] = res$StdError.Est
        est$time[est$mr_methods=="egger"] = T1-T0
        rm(res)
        # 8. contamination mixture
        T0 = proc.time()[3]
        res = MendelianRandomization::mr_conmix(mr.obj)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="conmix"] = res$Estimate
        CIlength = res$CIUpper-res$CILower
        if (length(CIlength)>1) print("conmix multimodal")
        est$se.estimate[est$mr_methods=="conmix"] = sum(CIlength)/1.96/2 ## Caution: this may be problematic (Qi&Chatterjee2021)
        est$time[est$mr_methods=="conmix"] = T1-T0
        rm(res)
        # 9. MRMix
              # theta_temp_vec = seq(-0.5,0.5,by=0.01)
        T0 = proc.time()[3]
        res = MRMix::MRMix(betahat_x = my_data_harm$beta.bmi, 
                          betahat_y = my_data_harm$beta.gbc, 
                          sx =my_data_harm$se.bmi, 
                          sy = my_data_harm$se.gbc)
        res_se = MRMix::MRMix_se(betahat_x = my_data_harm$beta.bmi, 
                          betahat_y = my_data_harm$beta.gbc, 
                          sx =my_data_harm$se.bmi, 
                          sy = my_data_harm$se.gbc, 
                          theta = res$theta, # estimate of causal effect, assuming the summary stats are standardized, theta represents increase in mean value of Y in s.d. unit of Y (for cont outcomes) or log-OR of Y (for binary outcomes)
                          pi0 = res$pi0, 
                          sigma2 = res$sigma2
                          )
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="MRMix"] = res$theta
        est$se.estimate[est$mr_methods=="MRMix"] = res_se
        est$time[est$mr_methods=="MRMix"] = T1-T0
        rm(res, res_se)
        # 10. MR-RAPS  
        ## Warning: The estimated overdispersion parameter is very small. Consider using the simple model without overdispersion.
        T0 = proc.time()[3]
        res = mr.raps::mr.raps.overdispersed.robust(b_exp = my_data_harm$beta.bmi, 
                                                    b_out = my_data_harm$beta.gbc, 
                                                    se_exp = my_data_harm$se.bmi, 
                                                    se_out = my_data_harm$se.gbc, 
                                                    loss.function = "huber", 
                                                    k = 1.345, 
                                                    initialization = c("l2"), 
                                                    suppress.warning = FALSE, 
                                                    diagnosis = FALSE, 
                                                    niter = 20, 
                                                    tol = .Machine$double.eps^0.5)
        T1 = proc.time()[3]
        est$estimate[est$mr_methods=="RAPS"] = res$beta.hat
        est$se.estimate[est$mr_methods=="RAPS"] = res$beta.se
        est$time[est$mr_methods=="RAPS"] = T1-T0
        rm(res)

est %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  kable(digits=3, caption = "MR Results for GBC (outcome) using genetic variants as instrumental variables for BMI") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria")

saveRDS(est, paste0("../output/Rdata/", Sys.Date(), "_est.rds"))
```

@@

```{r simulatesimulatesimulate, warning=FALSE}
# data FOR simulation in simulation script
saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))
sim_vars <- list(n=n, colnames_pval=colnames_pval)
saveRDS(sim_vars, paste0("../output/Rdata/", Sys.Date(), "_sim_vars.rds"))

## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

@@

```{r calculate-performance-metrics}
bias <- function(thetaobs,theta) mean(thetaobs)- theta
mse <- function(thetaobs, theta) mean((thetaobs-theta)^2)

@@

## get performance metrics
funs <- c(bias = bias, mse = mse)
args <- list(theta = est$estimate[est$mr_methods == "conmix"]) # trim argument non-matching and ignored for median

performance_metrics <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

@@

```{r plot-performance-metrics-bias-mse}
#BIAS
ggplot(performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  theme_few() -> biasplot

#MSE
ggplot(performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  theme_few() -> mseplot

ggarrange(biasplot, mseplot) ->bias_mse_plot

filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_bias_mse.png")
ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

```{r plot-performance-metrics-boxplot}
# compare distribution of simulated thetas against theta_324000
boxplot_dat <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = format(as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")), scientific=FALSE))

ggplot(boxplot_dat, aes(x=forcats::fct_rev( as.factor(theta_sim_numeric)), y=value)) +
  geom_boxplot()+
  geom_jitter(width=0.1,alpha=0.2)+
  geom_hline(yintercept=  args$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = "300000", y = args$theta+0.5,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
  scale_x_discrete(name = paste0("Size of sample ", as.roman(1)),  breaks = c(" 50000", "100000", "150000", "200000", "250000", "300000"), )+ 
  ylab(expression(paste(theta[sim], " with ", n[sim]== 25 ) )  ) +
  labs(title = "Estimates from beta simulation",
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       )+
  coord_flip()+
  theme_few() -> simplot_betas
simplot_betas

filename_simplot_betas <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_betas.png")
ggsave(filename = filename_simplot_betas, plot = simplot_betas, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated

>>>>

t(filter_FTO) %>% kable() %>% 
  kable_styling(font_size=10)
```

@@

# Dual Y axis: we have 284 IVs, scale them to 5% (y-axis [0;5%]): 3/284 
## https://r-graph-gallery.com/line-chart-dual-Y-axis-ggplot2.html
scale_factor <- 4.5/284
df_cum_expl_var <- df_cum_expl_var %>% 
  mutate(
    cum_expl_varX = cum_expl_varX *100, # in percent 
    cum_expl_varX2 = cum_expl_varX2 *100,
    cum_expl_varU = cum_expl_varU *100,
    cum_expl_varY = cum_expl_varY *100,
    count_IVs_scaled = count_IVs*scale_factor)
```

@@

```{r MendelianRandomization-analysis, warning=FALSE}
# outsourced calculation to `perform_mr.R`
# data FOR estimates in `perform_mr.R` script and simulation in `simstudy.R` script
saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))

## load results
est <- readRDS(file = dplyr::last(list.files("../output/Rdata/", pattern = "_est.rds", full.names = TRUE)))

est %>% 
  mutate(OR=exp(estimate), CI.lower=exp(estimate-se.estimate),CI.upper=exp(estimate+se.estimate)) %>%  
  kable(digits=3, caption = "MR Results for GBC (outcome) using genetic variants as instrumental variables for BMI") %>% 
  kable_classic(full_width = FALSE, html_font = "Cambria")
```

@@

```{r simulatesimulatesimulate, warning=FALSE}
# save simulation-vars for simulation `simstudy.R` script
sim_vars <- list(n=n, colnames_pval=colnames_pval)
saveRDS(sim_vars, paste0("../output/Rdata/", Sys.Date(), "_sim_vars.rds"))
## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

@@

```{r calculate-performance-metrics}
# fns
bias <- function(thetaobs,theta, ...) mean(thetaobs)- theta
mse <- function(thetaobs, theta, ...) mean((thetaobs-theta)^2)
emp_se <- function(nsim, thetaobs, theta, ...) sqrt( 1/(nsim-1) * sum((thetaobs-mean(thetaobs))^2) )  # == sd

@@

## get performance metrics    # https://stackoverflow.com/questions/47415072/pass-multiple-functions-to-purrrmap
funs <- c(mean = mean, bias = bias, mse = mse, emp_se=emp_se)
args <- list(theta = est$estimate[est$mr_methods == "conmix"], nsim=nrow(est_sim)) # trim argument non-matching and ignored for median

performance_metrics <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

# est_sim %>%    # equivalent to `emp_se()` function, but `sd()` misses dotdotdot argument 
#   select(!!!(colname_theta)) %>% 
#   map_dbl(.f = ~sd(.))
```

```{r further-metrics}
# coverage
coverage <- function(thetaobs, thetaobs_se, theta, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  coverage <- mean(lower_ci <= theta & upper_ci >= theta)
  return(coverage)
}
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}

type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

coverage_calc <- c()
coverage_bias_eliminated_calc <- c()
type1error_calc <- c()
for (i in 1:length(sample_size_filtered)) {
  sample_size <- sample_size_filtered[i]
  col_theta <- paste0("theta_sim_", format(sample_size, scientific = FALSE))
  col_theta_se <- paste0("theta_se_sim_", format(sample_size, scientific = FALSE))
  col_mr_pval <- paste0("mr_pval_", format(sample_size, scientific = FALSE))

  coverage_calc[i] <- coverage(thetaobs = est_sim[col_theta], thetaobs_se = est_sim[col_theta_se], theta = est$estimate[est$mr_methods == "conmix"])
  coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_theta]], thetaobs_se = est_sim[[col_theta_se]])
  type1error_calc[i] <- type1error(est_sim[[col_mr_pval]])
}

performance_metrics <- performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(coverage_calc, coverage_bias_eliminated_calc, type1error_calc)) %>% 
  as_tibble()
```

@@

```{r boxplot-theta-sim-distribution, fig.height=6, fig.width=10}
# compare distribution of simulated thetas against theta_324000
boxplot_dat <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  pivot_longer(cols = everything(), names_to = "theta_sim") %>% 
  mutate(theta_sim_numeric = format(as.numeric(stringr::str_extract(string =theta_sim, pattern = "\\d+")), scientific=FALSE))

ggplot(boxplot_dat, aes(x=forcats::fct_rev( as.factor(theta_sim_numeric)), y=value)) +
  geom_boxplot()+
  geom_jitter(width=0.1,alpha=0.2)+
  geom_hline(yintercept=  args$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = "300000", y = args$theta+0.5,
           label= expression( paste("ref: ", theta[X] ))  , 
           color= ggthemes_data$few$colors$Dark[9,2][[1]]
             )+
  scale_x_discrete(name = paste0("Size of sample ", as.roman(1)),  breaks = c(" 50000", "100000", "150000", "200000", "250000", "300000"), )+ 
  ylab(expression(paste(theta[sim], " with ", n[sim]== 25 ) )  ) +
  labs(title = "Estimates from beta simulation",
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       )+
  coord_flip()+
  theme_few() -> simplot_thetas
simplot_thetas

### same plot as above, but from already calculated performance metrics theta_mean + theta_sd
ggplot(performance_metrics, aes(x=N, y=mean))+ 
  geom_point()+
  geom_hline(yintercept=  args$theta, col=ggthemes_data$few$colors$Dark[9,2][[1]], alpha=0.6, linetype=2, size=0.8)+
  annotate(geom = "text", x = 300000, y = args$theta+0.25,
         label= expression( paste("ref: ", theta[X] ))  , 
         color= ggthemes_data$few$colors$Dark[9,2][[1]]
           )+
  geom_errorbar(aes(ymin=mean-emp_se, ymax=mean+emp_se), 
                width=3000, # x-axis dimension
                position = "dodge")+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Mean thetas")+
  labs(title = "Simulated Thetas with Empirical Standard Error")+
  theme_few() -> simplot_thetas2
simplot_thetas2

filename_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_thetas.png")
ggsave(filename = filename_simplot_thetas, plot = simplot_thetas, 
       width = 10, height = 6, 
       units = "in"  # default
       )
filename_simplot_thetas2 <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_thetas2.png")
ggsave(filename = filename_simplot_thetas2, plot = simplot_thetas2, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

```{r plot-performance-metrics-bias-mse, fig.height=6, fig.width=14}
#BIAS
ggplot(performance_metrics, aes(x=N, y=bias))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("Bias")+
  labs(title = "Bias with Empirical Standard Error")+
  theme_few() -> biasplot

#MSE
ggplot(performance_metrics, aes(x=N, y=mse))+ 
  geom_point()+
  scale_x_continuous(labels = comma)+
  xlab("Size of Sample I")+
  ylab("MSE")+
  labs(title = "MSE")+
  theme_few() -> mseplot

ggarrange(biasplot, mseplot) ->bias_mse_plot
bias_mse_plot

filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_bias_mse.png")
ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot, 
       width = 14, height = 6, 
       units = "in"  # default
       )
```

@@

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated
plot_pve_simulated
